Delocalization of Eigenvectors in Random Matrices

### 2025-03-24 Draft.tex
up to p.32

In this section we will state all of the inequalities and stochastic bounds we will need for control of our SDE terms. Their rigorous justification is presented in the \hyperref[sec:appendix]{Appendix}. From now on, for the sake of brevity we will define $\eta_s = |\im w_s|$ and $\eta_t = |\im w_t|$, the notation of which includes the indexing with any particular time instantiation $t_0\in [0, 1]$. With this, let us state

@@

\item  $\sup_x\sum_{y}|G_{xy}|\lesssim W^{\frac{1}{2}+\epsilon}\eta_{s}^{-\frac{3}{4}}$ per \hyperref[lemma-b1]{Lemma B.1}.

\item $\max_{x,y}\left\vert G_{xy} - \delta_{xy}m(z)\right\vert\lesssim W^{-\frac{1}{2}}\eta_s^{-\frac{1}{4}}$ per  \hyperref[lemma-b2]{Lemma B.2}.

@@

\newpage
\section{Bounds on Flow Terms}
\label{sec:drift}
In this section, our goal is to control the three terms of the fluctuations between the $T_{xy}$ and $\Theta_{xy}$ matrices. The squared $\mathcal{E}_t^S$ and $M$-term $\mathcal{E}_t^M$ of the flow SDE can be handled using the resolvent bounds we derived earlier, along with standard martingale calculus. However, the drift term $\mathcal{E}^{D}_t$ requires extra care. For it, we will follow Dubova and Yang's derivation closely, which employs the graphical perturbation methods developed by Bourgade, Yau and Yin, in their self-energy renormalization paper \cite{38}. More specifically, we will use Definition 17  \cite{bandSDE} for the diagrammatic notation of a standard oriented graph:
\vspace{0.255 cm}
\begin{boxt}{Definition 2: (Diagrammatic notation)}\label{def2}
\begin{itemize}
\item Each vertex will be assigned a label, corresponding to a matrix index $\alpha \in \{1, \cdots, N\}$. 
\item Each blue-colored loop \textcolor{blue}{$\circlearrowright$}, regardless of direction, represents a term $G_s(z)_{\alpha\alpha} - m(z)$;
\item A solid blue edge  $\alpha\textcolor{blue}{\longrightarrow}\beta$ represents a factor of $G_s(z)_{\alpha\beta}$, whereas a red $\alpha\textcolor{red}{\longrightarrow}\beta$ one is $\overline{G_s(z)_{\alpha\beta}}$;
\item A black wavy edge $\alpha\leftrightsquigarrow \beta$ represents $S_{\alpha\beta}$, whereas $\alpha\textcolor{blue}{\leftrightsquigarrow} \beta$ is $B_{\alpha\beta} = (I-sm(z)^2S)^{-1}$; 
\item A double edge $\alpha =\!=\!=\!=\beta$ represents $\{\text{Id}+(t-s)\Theta_t\}S^{1/2}$, which commute as shown before;
\end{itemize}
\end{boxt}
Having defined the diagrammatic notation, we can now present the main operation that will allow the bounding of the drift term, namely Lemma 16 \cite{bandSDE}, which lists the loop expansion (Lemma 3.5 \cite{38}) and the regular vertex expansion (Lemma 3.14 \cite{38}):

@@

\draw[thick, double] (a) -- (x);
\draw[blue, ->] (x) to (u);
\draw[wavy] (u) -- (v);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, ->] (u) to (beta);
\draw[blue, ->] (alpha) to (y);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, <-] (alpha) to [bend left=40] (beta);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{4, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{xu}  S_{uv} B_{v\alpha}S_{\alpha\beta}G_{\beta\alpha}G_{u\beta}G_{\alpha y}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Observe that in all cases we have a vertex $u$ that has one incoming and one outgoing blue edge, implying that we can again apply the regular vertex expansion w.r.t to $u$. For both $\mathcal{G}_{1, s}$ and $\mathcal{G}_{2, s}$ the incoming and outgoing edges are the same, starting and ending at $x$ and $y$, respectively. For $i=3$ and $i=4$ we have a different incoming or outgoing edge, so the corresponding expansion will require slight reformulation. Accounting for this fact, we get the following identities: 
\begin{itemize}
\item For $\mathcal{G}_{1, s}$ and $\mathcal{G}_{2, s}$: \begin{equation*}
G_{xu}G_{uy}f(G) = mB_{uy}G_{xy} f(G) + sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{x\gamma}(G_{\delta\delta}-m)G_{\gamma y} f(G)
\end{equation*}
$$+sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{x\delta}(G_{\gamma\gamma}-m)G_{\delta y}f(G)-sm\sum_{\gamma\beta=1}^N B_{u\gamma}S_{\gamma\delta}G_{x\gamma}G_{\delta y}\partial_{H_{\delta \gamma}}(f(G))$$
\item For $\mathcal{G}_{3, s}$:
\begin{equation*}
G_{\alpha u}G_{uy}f(G) = mB_{uy}G_{\alpha y} f(G) + sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{\alpha\gamma}(G_{\delta\delta}-m)G_{\gamma y} f(G)
\end{equation*}
$$+sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{\alpha\delta}(G_{\gamma\gamma}-m)G_{\delta y}f(G)-sm\sum_{\gamma\delta=1}^N B_{u\gamma}S_{\gamma\delta}G_{\alpha\gamma}G_{\delta y}\partial_{H_{\delta \gamma}}(f(G))$$
\item For $\mathcal{G}_{4, s}$:
\begin{equation*}
G_{xu}G_{u\beta}f(G) = mB_{u\beta}G_{x\beta} f(G) + sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{x\gamma}(G_{\delta\delta}-m)G_{\gamma \beta} f(G)
\end{equation*}
$$+sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{x\delta}(G_{\gamma\gamma}-m)G_{\delta \beta}f(G)-sm\sum_{\gamma\delta=1}^N B_{u\gamma}S_{\gamma\delta}G_{x\gamma}G_{\delta \beta}\partial_{H_{\delta \gamma}}(f(G))$$
\end{itemize}
As we noted earlier, each of the former identities can be represented as the sum of independent subraphs, such that for $i=1, 2, 3, 4$, we have:
$$\mathcal{G}_{i, s} = m\mathcal{G}_{i0, s}+sm\mathcal{G}_{i1,s}+sm\mathcal{G}_{i2, s}-sm\mathcal{G}_{i3,s}^{(1)}-sm\mathcal{G}_{i3,s}^{(2)}-sm\mathcal{G}_{i3,s}^{(3)},$$
We will begin by focusing our attention on the first three terms for a fixed $i=1, 2, 3, 4$, namely $\mathcal{G}_{ij}$ for $j=0, 1, 2$. For brevity, let us define $\eta_s = \left\vert \text{Im}w_s\right\vert = \left\vert \text{Im}[z+(1-t)m(z)]\right\vert$. 
Using the estimates we defined in Section 5, we can simplify each of the resulting subgraph, starting with $j=0$:
\subsubsection*{Size estimates for $\mathcal{G}_{10, s}$}
Following diagrammatic notation, each of the $B_{uy_i}G_{x_iy_i}f(G)$ terms becomes:
\begin{center}
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (2, 0) {x};
\node (u) at (4, 0) {u};
\node (v) at (4, 1) {v};
\node (y) at (6, 0) {y};
\node (b) at (8, 0) {b};
\node (alpha) at (4, 2) {$\alpha$};
\node (beta) at (6, 2) {$\beta$};

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[wavy, blue] (u) -- (y);
\draw[thick, double] (y) -- (b);
\draw[red, ->] (x) to[bend right=15	] (y);
\draw[blue, ->](x) to [bend right=35] (y);
\draw[blue, ->] (alpha) to[out=200, in=150, loop] (alpha);
\draw[blue, ->] (beta) to[out=0, in=40, loop] (beta);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{10, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}}S_{uv}B_{v\alpha}(G_{\alpha\alpha}-m)S_{\alpha\beta}(G_{\beta\beta}-m)B_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
We can apply estimate $(2)$ to the two loops around $\alpha$ and $\beta$, as well as estimate $(1)$ to the red edge connecting $x$ and $y$. From this, we receive three multiplicative terms $O(W^{\delta_\sto/20}W^{-1/2}\eta_s^{-1/4})$, i.e combined it yields a term $O(W^{3\delta_\sto/20}W^{-3/2}\eta_s^{-3/4})$. By estimate $(5)$, we can sum all the wavy lines out in order $\beta, \alpha, v,$ and finally $u$ for a $O(1)$ term, keeping our earlier estimate. We can stop here by leaving the connected component that is a double line from $a$ to $x$, a blue line from $x$ to $y$ and another double line from $y$ to $b$, i.e: $\mathcal{G}_{10, s}\lesssim W^{3\delta_\sto/20}W^{-3/2}\eta_s^{-3/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (u) -- (y);
\draw[blue, ->] (x) to [bend right=20] (y);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[red, ->] (beta) to (y);
\draw[red, ->] (x) to[bend left=20] (alpha);
\draw[blue, ->] (beta) to[bend left=30] (alpha);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{20, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{x\alpha}}G_{xy} \overline{G_{\beta y}} S_{uv} B_{v\alpha}S_{\alpha\beta}G_{\beta\alpha}B_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Repeating the same process as before, we bound all three red lines using estimate $(2)$ and sum over the wavy edges in the same order $(\beta, \alpha, v$, and $u$), s.t. we get the same bound as above:\\
$\mathcal{G}_{20, s}\lesssim W^{3\delta_\sto/20}W^{-3/2}\eta_s^{-3/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (u) to (y);
\draw[blue, ->] (alpha) to (y);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, <-] (alpha) to[bend right=30] (beta);
\draw[blue, ->] (x) to[bend left=60] (beta);
\draw[red, ->] (x) to [bend right=20] (y);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{30, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{x\beta}S_{uv} B_{v\alpha}  S_{\alpha\beta}G_{\beta\alpha}G_{uy} B_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Here, we eliminate first the edges  $\beta\textcolor{red}{\rightarrow}\alpha$ and $\alpha\textcolor{blue}{\rightarrow} y$ using estimate $(2)$, giving us a $O(W^{\delta_\sto/10}W^{-1}\eta_s^{-1/2})$ term. Due to the edge from $x\textcolor{blue}{\rightarrow}\beta$, we are not going to be summing $\alpha\leadsto\beta$ over $S_{ab}$ entries because it serves as a multiplicative term to the blue edge $x\textcolor{blue}{\rightarrow}\beta$. For this reason, we will apply the individual $S_{ab}\lesssim W^{-1}$ bound, s.t now summing over $x\textcolor{blue}{\rightarrow}\beta$ with estimate $(1)$ gives us a combined bound $O(W^{\delta_\sto/20}W^{\frac{1}{2}+\epsilon}\eta_s^{-3/4})$. Finally, by summing over the remaining wavy edges, starting with $\alpha, v$ and then $u$, due to the $O(1)$ term (estimate $(5)$), we get an estimate of the form: $\mathcal{G}_{30, s}\lesssim W^{3\delta_\sto/20}W^{-\frac{1}{2}+\epsilon}\eta_s^{-5/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, wavy] (u) to (beta);
\draw[blue, ->] (alpha) to (y);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, <-] (alpha) to [bend left=15] (beta);
\draw[blue, ->] (x) to[bend left=60] (beta);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{4, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{x\beta}  S_{uv} B_{v\alpha}S_{\alpha\beta}G_{\beta\alpha}B_{u\beta}G_{\alpha y}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Here, we bound first the inner edges $\alpha\textcolor{blue}{\rightarrow} y$ and $\beta\textcolor{red}{\rightarrow}\alpha$, we get by estimate $(2)$ a combined term $\lesssim O(W^{\delta_\sto/10}W^{-1}\eta_{s}^{-1/2})$. Again, by the same logic as above, we have to account for the individual term $\alpha\leadsto\beta$ instead of summing over it, retaining a $O(W^{-1})$ term. By applying estimate $(1)$ for the edge $x\textcolor{blue}{\rightarrow}\beta$ and summing over the remaining wavy lines, we get the same bound as above, namely: 
$\mathcal{G}_{40, s}\lesssim  W^{3\delta_\sto/20}W^{-\frac{1}{2}+\epsilon}\eta_s^{-5/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

@@

\subsubsection*{Size estimates for $\max_{i=1, \cdots, 4}\mathcal{G}_{40, s}$}

@@

\noindent Here, we will repeat an equivalent procedure as above, bounding the loop at $\delta$ and the edges $x\textcolor{red}{\rightarrow}\alpha$, $\beta\textcolor{blue}{\rightarrow}\alpha$ and $\beta\textcolor{red}{\rightarrow}y$ , getting a bound $O(W^{\delta_\sto/5}W^{-2}\eta_s^{-1})$. Then, we can sum the wavy lines with estimate $(5)$, getting an equivalent bound as above:
$\mathcal{G}_{21, s}\lesssim W^{\delta_\sto/5}W^{-2}\eta_s^{-1}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (gamma) at (2, 0) {$\gamma$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};

>>>>

In this section we will state all of the inequalities and stochastic bounds we will need for control of our SDE terms. The \hyperref[sec:appendix]{Appendix} includes the proofs of some, and the references for the rest. From now on, for the sake of brevity we will define $\eta_s = |\im w_s|$ and $\eta_t = |\im w_t|$, the notation of which includes the indexing with any particular time instantiation $t_0\in [0, 1]$. With this, let us state

@@

\item  $\sup_x\sum_{y}|G_{xy}|\lesssim W^{\frac{\delta\sto}{20}} W^{\frac{1}{2}+\epsilon}\eta_{s}^{-\frac{3}{4}}$ per \hyperref[lemma-b1]{Lemma B.1}.

\item $\max_{x,y}\left\vert G_{xy} - \delta_{xy}m(z)\right\vert\lesssim W^{\frac{\delta_\sto}{20}}W^{-\frac{1}{2}}\eta_s^{-\frac{1}{4}}$ per  \hyperref[lemma-b2]{Lemma B.2}.

@@

\newpage
\section{Bounds on Flow Terms}
\label{sec:drift}
In this section, our goal is to control the three stopped terms of the fluctuations between the $T_{xy}$ and $\Theta_{xy}$ matrices. The squared $\mathcal{E}_t^{S, \sto}$ and martingale term $\mathcal{E}_t^{M, \sto}$ of the flow SDE can be handled using the resolvent bounds we stated in the last section, along with standard martingale calculus. However, the drift term $\mathcal{E}^{D, \sto}_t$ requires extra care. For it, we will follow Dubova and Yang's derivation closely, which employs the graphical perturbation methods developed by Bourgade, Yau and Yin, in their self-energy renormalization paper \cite{38}. More specifically, we will use Definition 17  \cite{bandSDE} for the diagrammatic notation of a standard oriented graph:
\vspace{0.255 cm}
\begin{boxt}{Definition 2: (Diagrammatic notation)}\label{def2}
\begin{itemize}
\item Each vertex will be assigned a label, corresponding to a matrix index $\alpha \in \{1, \cdots, N\}$. 
\item Each blue-colored loop \textcolor{blue}{$\circlearrowright$} at $\alpha$, regardless of direction, represents a term $G_s(z)_{\alpha\alpha} - m(z)$;
\item A solid blue edge  $\alpha\textcolor{blue}{\longrightarrow}\beta$ represents a factor of $G_s(z)_{\alpha\beta}$, whereas a red $\alpha\textcolor{red}{\longrightarrow}\beta$ one is $\overline{G_s(z)_{\alpha\beta}}$;
\item A black wavy edge $\alpha\leftrightsquigarrow \beta$ represents $S_{\alpha\beta}$, whereas $\alpha\textcolor{blue}{\leftrightsquigarrow} \beta$ is $B_{\alpha\beta} = (I-sm(z)^2S)^{-1}$; 
\item A double edge $\alpha =\!=\beta$ represents $\{\text{Id}+(t-s)\Theta_t\}S^{1/2}$;
\end{itemize}
\end{boxt}
Having defined the diagrammatic notation, we can now present the main operation that will allow for the bounding of the drift term, namely Lemma 16 \cite{bandSDE}, which lists the loop expansion (Lemma 3.5 \cite{38}) and the regular vertex expansion (Lemma 3.14 \cite{38}):

@@

\draw[thick, double] (a) -- (x);
\draw[blue, ->] (x) to (u);
\draw[wavy] (u) -- (v);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, ->] (u) to (beta);
\draw[blue, ->] (alpha) to (y);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, <-] (alpha) to [bend left=40] (beta);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{4, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{xu}  S_{uv} B_{v\alpha}S_{\alpha\beta}G_{\beta\alpha}G_{u\beta}G_{\alpha y}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Observe that in all cases we have a vertex $u$ that has one incoming and one outgoing blue edge, implying that we can again apply the regular vertex expansion w.r.t to $u$. For both $\mathcal{G}_{1, s}$ and $\mathcal{G}_{2, s}$ the incoming and outgoing edges are the same, starting and ending at $x$ and $y$, respectively. For $i=3$ and $i=4$ we have a different incoming or outgoing edge, so the corresponding expansion will require slight reformulation. Accounting for this fact, we get the following identities: 
\begin{itemize}
\item For $\mathcal{G}_{1, s}$ and $\mathcal{G}_{2, s}$: \begin{equation*}
G_{xu}G_{uy}f(G) = mB_{uy}G_{xy} f(G) + sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{x\gamma}(G_{\delta\delta}-m)G_{\gamma y} f(G)
\end{equation*}
$$+sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{x\delta}(G_{\gamma\gamma}-m)G_{\delta y}f(G)-sm\sum_{\gamma\beta=1}^N B_{u\gamma}S_{\gamma\delta}G_{x\gamma}G_{\delta y}\partial_{H_{\delta \gamma}}(f(G))$$
\item For $\mathcal{G}_{3, s}$:
\begin{equation*}
G_{\alpha u}G_{uy}f(G) = mB_{uy}G_{\alpha y} f(G) + sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{\alpha\gamma}(G_{\delta\delta}-m)G_{\gamma y} f(G)
\end{equation*}
$$+sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{\alpha\delta}(G_{\gamma\gamma}-m)G_{\delta y}f(G)-sm\sum_{\gamma\delta=1}^N B_{u\gamma}S_{\gamma\delta}G_{\alpha\gamma}G_{\delta y}\partial_{H_{\delta \gamma}}(f(G))$$
\item For $\mathcal{G}_{4, s}$:
\begin{equation*}
G_{xu}G_{u\beta}f(G) = mB_{u\beta}G_{x\beta} f(G) + sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{x\gamma}(G_{\delta\delta}-m)G_{\gamma \beta} f(G)
\end{equation*}
$$+sm\sum_{\gamma\delta=1}^N B_{u\gamma} S_{\gamma\delta} G_{x\delta}(G_{\gamma\gamma}-m)G_{\delta \beta}f(G)-sm\sum_{\gamma\delta=1}^N B_{u\gamma}S_{\gamma\delta}G_{x\gamma}G_{\delta \beta}\partial_{H_{\delta \gamma}}(f(G))$$
\end{itemize}
As we noted earlier, each of the former identities can be represented as the sum of independent subraphs, such that for $i=1, 2, 3, 4$, we have:
$$\mathcal{G}_{i, s} = m\mathcal{G}_{i0, s}+sm\mathcal{G}_{i1,s}+sm\mathcal{G}_{i2, s}-sm\mathcal{G}_{i3,s}^{(1)}-sm\mathcal{G}_{i3,s}^{(2)}-sm\mathcal{G}_{i3,s}^{(3)},$$
We will begin by focusing our attention on the first three terms for a fixed $i=1, 2, 3, 4$, namely $\mathcal{G}_{ij}$ for $j=0, 1, 2$. Using the estimates we defined in Section 5, we can simplify each of the resulting subgraph, starting with $j=0$:\newpage
\subsubsection*{Size estimates for $\mathcal{G}_{10, s}$}
Following diagrammatic notation, each of the $B_{uy_i}G_{x_iy_i}f(G)$ terms becomes:
\begin{center}
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (2, 0) {x};
\node (u) at (4, 0) {u};
\node (v) at (4, 1) {v};
\node (y) at (6, 0) {y};
\node (b) at (8, 0) {b};
\node (alpha) at (4, 2) {$\alpha$};
\node (beta) at (6, 2) {$\beta$};

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[wavy, blue] (u) -- (y);
\draw[thick, double] (y) -- (b);
\draw[red, ->] (x) to[bend right=15	] (y);
\draw[blue, ->](x) to [bend right=35] (y);
\draw[blue, ->] (alpha) to[out=200, in=150, loop] (alpha);
\draw[blue, ->] (beta) to[out=0, in=40, loop] (beta);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{10, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}}S_{uv}B_{v\alpha}(G_{\alpha\alpha}-m)S_{\alpha\beta}(G_{\beta\beta}-m)B_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
We can apply estimate $(E2)$ to the two loops around $\alpha$ and $\beta$, as well as estimate $(E1)$ to the red edge connecting $x$ and $y$. From this, we receive three multiplicative terms $O(W^{\delta_\sto/20}W^{-1/2}\eta_s^{-1/4})$, i.e combined it yields a term $O(W^{3\delta_\sto/20}W^{-3/2}\eta_s^{-3/4})$. By estimate $(E5)$, we can sum all the wavy lines out in order $\beta, \alpha, v,$ and finally $u$ for a $O(1)$ term, keeping our earlier term. We can stop here by leaving the connected component that is a double line from $a$ to $x$, a blue line from $x$ to $y$ and another double line from $y$ to $b$, i.e: $\mathcal{G}_{10, s}\lesssim W^{3\delta_\sto/20}W^{-3/2}\eta_s^{-3/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (u) -- (y);
\draw[blue, ->] (x) to [bend right=20] (y);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[red, ->] (beta) to (y);
\draw[red, ->] (x) to[bend left=20] (alpha);
\draw[blue, ->] (beta) to[bend left=30] (alpha);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{20, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{x\alpha}}G_{xy} \overline{G_{\beta y}} S_{uv} B_{v\alpha}S_{\alpha\beta}G_{\beta\alpha}B_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Repeating the same process as before, we bound all three red lines using estimate $(E2)$ and sum over the wavy edges in the same order $(\beta, \alpha, v$, and $u$), s.t. we get the same bound as above:\\
$\mathcal{G}_{20, s}\lesssim W^{3\delta_\sto/20}W^{-3/2}\eta_s^{-3/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[blue, wavy] (u) to (y);
\draw[blue, ->] (alpha) to (y);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, <-] (alpha) to[bend right=30] (beta);
\draw[blue, ->] (x) to[bend left=60] (beta);
\draw[red, ->] (x) to [bend right=20] (y);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{30, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{x\beta}S_{uv} B_{v\alpha}  S_{\alpha\beta}G_{\beta\alpha}G_{uy} B_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Here, we eliminate first the edges  $\beta\textcolor{red}{\rightarrow}\alpha$ and $\alpha\textcolor{blue}{\rightarrow} y$ using estimate $(E2)$, giving us a $O(W^{\delta_\sto/10}W^{-1}\eta_s^{-1/2})$ term. Due to the edge from $x\textcolor{blue}{\rightarrow}\beta$, we are cannot sum $\alpha\leadsto\beta$ over $S_{ab}$ entries because it serves as a multiplicative term to the blue edge $x\textcolor{blue}{\rightarrow}\beta$. For this reason, we will apply the individual $S_{ab}\lesssim W^{-1}$ bound, s.t now summing over $x\textcolor{blue}{\rightarrow}\beta$ with estimate $(E1)$ gives us a combined bound $O(W^{\delta_\sto/20}W^{\frac{1}{2}+\epsilon}\eta_s^{-3/4})$. Finally, by summing over the remaining wavy edges, starting with $\alpha, v$ and then $u$, due to the $O(1)$ term (estimate $(E5)$), we get an estimate of the form: $\mathcal{G}_{30, s}\lesssim W^{3\delta_\sto/20}W^{-\frac{1}{2}+\epsilon}\eta_s^{-5/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

@@

\draw[thick, double] (a) -- (x);
\draw[wavy] (u) -- (v);
\draw[thick, double] (y) -- (b);
\draw[wavy, blue] (v) to (alpha);
\draw[wavy] (alpha) to (beta);
\draw[blue, wavy] (u) to (beta);
\draw[blue, ->] (alpha) to (y);
\draw[red, ->] (x) to [bend right=20] (y);
\draw[blue, <-] (alpha) to [bend left=15] (beta);
\draw[blue, ->] (x) to[bend left=60] (beta);
\end{tikzpicture}
\begin{equation*}
\mathcal{G}_{4, s}(z)_{ab} = \left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_{xy}} G_{x\beta}  S_{uv} B_{v\alpha}S_{\alpha\beta}G_{\beta\alpha}B_{u\beta}G_{\alpha y}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{yb}
\end{equation*}
\end{center}
Here, we bound first the inner edges $\alpha\textcolor{blue}{\rightarrow} y$ and $\beta\textcolor{red}{\rightarrow}\alpha$, we get by estimate $(E2)$ a combined term $\lesssim O(W^{\delta_\sto/10}W^{-1}\eta_{s}^{-1/2})$. Again, by the same logic as above, we have to account for the individual term $\alpha\leadsto\beta$ instead of summing over it, retaining a $O(W^{-1})$ term. By applying estimate $(E1)$ for the edge $x\textcolor{blue}{\rightarrow}\beta$ and summing over the remaining wavy lines, we get the same bound as above, namely: 
$\mathcal{G}_{40, s}\lesssim  W^{3\delta_\sto/20}W^{-\frac{1}{2}+\epsilon}\eta_s^{-5/4}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (y) at (2, 0) {y};
\node (b) at (3, 0) {b};

@@

\newpage
\subsubsection*{Size estimates for $\max_{i=1, \cdots, 4}\mathcal{G}_{40, s}$}

@@

\noindent Here, we will repeat an equivalent procedure as above, bounding the loop at $\delta$ and the edges $x\textcolor{red}{\rightarrow}\alpha$, $\beta\textcolor{blue}{\rightarrow}\alpha$ and $\beta\textcolor{red}{\rightarrow}y$ , getting a bound $O(W^{\delta_\sto/5}W^{-2}\eta_s^{-1})$. Then, we can sum the wavy lines with estimate $(E5)$, getting an equivalent bound as above:
$\mathcal{G}_{21, s}\lesssim W^{\delta_\sto/5}W^{-2}\eta_s^{-1}\times $
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (1, 0) {x};
\node (gamma) at (2, 0) {$\gamma$};
\node (y) at (3, 0) {y};
\node (b) at (4, 0) {b};
